### 2017-04-17 paper/oopsla17-submission/evaluation.tex
minor tweaks

\mypara{1. Data beats Algorithms}
Our main result is that for type error
localization, data is indeed unreasonably
effective \citep{halevy09}.
%
\toolname's most sophisticated
\emph{neural network}
based classifier's top-1 error
location blames the correct
sub-term 74\% of the time
which, a good 18 points
higher than the state of
the art \sherrloc's 56\%.
%
However, even \toolname's simple
\emph{logistic regression} based
classifier is correct 60\% of the time,
\ie 4 points better than \sherrloc.
%
When the top-3 locations are considered,
\toolname is correct 91\% of the time.

% \item \textbf
\mypara{2. Slicing is Critical}
%
However, data is effective \emph{only}
when irrelevant sub-terms have been
sliced out of consideration.
%
In fact, perhaps our most surprising
result is that type-error-slicing and
local syntax alone yields
a neural classifier that is 10 points
better than \ocaml and on par with
\sherrloc.
%
That is once we focus classifiers on
slices, local syntactic features
alone perform as well as the
state-of-the-art.

%\item \textbf
\mypara{3. Size doesn't matter, types do}
%
We find that (after slices)
contextual typing features
provide the biggest
improvement in accuracy.
%
Furthermore we find contextual syntax
features to be mostly (but not entirely)
redundant with typing features,
which supports the hypothesis that
the context's \emph{type} nicely
summarizes the properties of the
surrounding expressions.
%
Finally, we found that the \emph{size}
of the sub-expression was not very useful.
This was unexpected, as we thought
smaller expressions would be simpler, and
hence, more likely causes.

>>>>

\mypara{1. Data Beats Algorithms}
Our main result is that for type error
localization, data is indeed unreasonably
effective \citep{halevy09}.
%
\toolname's most sophisticated
\emph{neural network}-based
classifier's top-ranked
prediction blames the correct
sub-term 74\% of the time
which, a good 18 points
higher than the state of
the art \sherrloc's 56\%.
%
However, even \toolname's simple
\emph{logistic regression} based
classifier is correct 60\% of the time,
\ie 4 points better than \sherrloc.
%
When the top three predictions are considered,
\toolname is correct 91\% of the time.

% \item \textbf
\mypara{2. Slicing Is Critical}
%
However, data is effective \emph{only}
when irrelevant sub-terms have been
sliced out of consideration.
%
In fact, perhaps our most surprising
result is that type error slicing and
local syntax alone yields
a classifier that is 10 points
better than \ocaml and on par with
\sherrloc.
%
That is, once we focus our classifiers on
slices, purely syntactic features
perform as well as the
state-of-the-art.

%\item \textbf
\mypara{3. Size Doesn't Matter, Types Do}
%
We find that (after slices)
typing features
provide the biggest
improvement in accuracy.
%
Furthermore, we find contextual syntax
features to be mostly (but not entirely)
redundant with typing features,
which supports the hypothesis that
the context's \emph{type} nicely
summarizes the properties of the
surrounding expressions.
%
Finally, we found that the \emph{size}
of the sub-expression was not very useful.
This was unexpected, as we thought
smaller expressions would be simpler, and
hence, more likely causes.
